\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{capt-of}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}

\newcounter{boxctr}
\newcommand{\boxcaption}[1]{%
  \refstepcounter{boxctr}%
  \textbf{Box \theboxctr. #1}%
}

% Keep page bottoms visually aligned.
\flushbottom
% Slightly increase line spacing for better page fill/readability.
\setstretch{1.03}
% Harmonize spacing around floats/inline figures for a cleaner layout.
\setlength{\textfloatsep}{10pt plus 2pt minus 2pt}
\setlength{\floatsep}{8pt plus 2pt minus 2pt}
\setlength{\intextsep}{8pt plus 2pt minus 2pt}
\setlength{\abovecaptionskip}{4pt}
\setlength{\belowcaptionskip}{4pt}

\begin{document}

\title{A Case-Based Multi-Agent Framework for LLM Reasoning: Integrating Memory Retrieval with Debate and Reflection}

\titlerunning{Case-Based Multi-Agent Framework for LLM Reasoning}

\author{Xinyi Chang\inst{1}}
\authorrunning{X. Chang}
\institute{Communication University of China, China \\
\email{xian@cuc.edu.cn}}

\maketitle

\begin{abstract}
Large Language Models (LLMs) have demonstrated remarkable capabilities in complex reasoning, yet they remain susceptible to logical hallucinations and calculation errors, largely due to their reliance on zero-shot generative paradigms. To address this limitation, we propose a framework that integrates traditional Case-Based Reasoning (CBR) with a modern multi-agent architecture. Specifically, we map the classic 4R cycle (Retrieve, Reuse, Revise, Retain) into an LLM-driven collaborative system for mathematical reasoning tasks. Given a new problem, a retrieval module first extracts similar historical cases from a dedicated memory bank. A Generator agent then reuses these cases via few-shot prompting to produce an initial solution. To handle the revision phase, historically a bottleneck in CBR, we introduce an interactive mechanism with a Critic agent and a Judge agent that reflect on and correct the initial output. Finally, successful solutions are retained in the case base to improve future retrieval quality. We evaluate the framework on a 500-instance subset of GSM8K. Results reveal a key cost--performance trade-off: blanket multi-agent debate yields 91.2\% accuracy, while a learned post-hoc selector that adaptively routes between standard RAG and our debate module matches a strong RAG baseline (92.6\%). The oracle upper bound reaches 95.0\%, highlighting the potential of adaptively combining classical CBR principles with LLM multi-agent reasoning.

\keywords{Case-Based Reasoning \and Large Language Models \and Multi-Agent Systems \and Retrieval-Augmented Generation \and Automated Reasoning}
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_method}
\input{sections/04_experiments}
\input{sections/05_results}
\input{sections/06_conclusion}

\section*{Acknowledgments}
% Optional. Keep empty or add funding/collaboration credits.

\section*{Generative AI Statement}
The authors used generative AI tools to assist with language polishing, code prototyping, and figure scripting. All scientific claims, experimental design, implementation decisions, data analysis, and final manuscript content were reviewed and validated by the authors. The authors take full responsibility for the correctness and originality of this work.

\bibliographystyle{splncs04}
\bibliography{references}

\end{document}
