\section{Experimental Setup}

\subsection{Dataset and Protocol}
We evaluate on GSM8K (main configuration)~\cite{cobbe2021gsm8k}. The official training split (7,473 problems) is used exclusively as the historical case base for retrieval, without any parameter fine-tuning. To ensure comparability under limited budget, all methods are tested on a randomly sampled 500-instance subset of the test split with a fixed seed (seed~=~42). The primary metric is exact-match numeric accuracy on the final answer.

\vspace{-0.25em}
\subsection{Baselines}
\begin{itemize}
  \setlength{\itemsep}{2pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item \textbf{Zero-shot (B1).} Direct generation without retrieval or debate-based revision. This is a lower-bound reference for the backbone model.
  \item \textbf{Standard RAG (Baseline 2).} Retrieve+Reuse only: top-$K$ similar cases are inserted as few-shot exemplars, but no Critic/Judge revision is applied.
  \item \textbf{Ours (CBR + Multi-Agent, v5).} Full 4R pipeline with Generator--Critic--Judge collaboration, plus gated revise and fallback voting.
  \item \textbf{Ours + Learned Selector.} A post-hoc routing model that adaptively selects the final prediction from Standard RAG or Ours (v5, gated revise + fallback voting) for each instance.
\end{itemize}

\vspace{-0.35em}
\subsection{Implementation Details}
All agents use \texttt{gpt-4o-mini} through an OpenAI-compatible UniAPI endpoint. We set Generator temperature to 0.3, and Critic/Judge temperature to 0.0 for stable verification behavior. For retrieval, we use the \texttt{all-MiniLM-L6-v2} encoder from \texttt{sentence-transformers} with FAISS indexing and cosine similarity. Unless otherwise stated, top-$K=3$ cases are retrieved per query to construct few-shot prompts.
For Learned Selector evaluation, we report strict out-of-fold performance under 5-fold cross-validation: the selector is trained on four folds and evaluated on the held-out fold only. Features are derived from deployable traces (e.g., votes, revise flags, token statistics) and exclude any gold-answer information at inference time.

\vspace{-0.35em}
\subsection{Multi-Agent Prompt Design}
To improve reproducibility, Table~\ref{tab:agent_prompts} summarizes the role-specific system prompts used by our Generator, Critic, and Judge agents.

\begin{table}[!htbp]
\caption{System prompts for the multi-agent debate module.}
\label{tab:agent_prompts}
\centering
\small
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{p{0.16\linewidth}p{0.78\linewidth}}
\toprule
Agent Role & System Prompt Template \\
\midrule
Generator & ``You are an expert mathematical problem solver. You will be provided with a new math problem and a few historically solved cases that share similar underlying logic. Your task is to carefully study the provided cases and generate a step-by-step solution for the new problem. End your response with the final numerical answer.'' \\
Critic & ``You are a rigorous and skeptical mathematical reviewer. You are provided with a math problem and an initial solution proposed by another agent. Your task is to scrutinize the solution for any calculation errors, missed conditions, or logical fallacies. Do NOT solve the problem from scratch. If you find an error, point it out explicitly. If the solution is completely correct, output `No Errors Found'.'' \\
Judge & ``You are the final arbiter. You are provided with: (1) the original math problem, (2) an initial solution, and (3) a critique of that solution. Your task is to evaluate the critique. If the critique correctly identifies an error, recalculate the steps and provide the corrected final solution. If the critique is invalid, defend the initial solution. Output the definitive final numerical answer.'' \\
\bottomrule
\end{tabular}
\end{table}

